%-------------------------------------------------------------------------------
%	SECTION TITLE
%-------------------------------------------------------------------------------
\cvsection{Experience}


%-------------------------------------------------------------------------------
%	CONTENT
%-------------------------------------------------------------------------------
\begin{cventries}
%---------------------------------------------------------
  \cventry
    {Co-Founder} % Job title
    {Penguin Academy} % Organization
    {St. Gallen, Switzerland} % Location
    {Jan. 2019 - Present} % Date(s)
    {\href{https://penguin.academy}{penguin.academy}} % Link
    {
      \begin{cvitems} % Description(s) of tasks/responsibilities
      \item {Develop the Penguin strategy.}
      \item {Lead of the PenguinLab, an initiative that guides bootcamp alumna to work on client projects.}
      \item {Create technical content for Penguin Academy projects.}
      \end{cvitems}
    }
%---------------------------------------------------------
  \cventry
    {Co-Founder, CTO} % Job title
    {Datalab St. Gallen} % Organization
    {St. Gallen, Switzerland} % Location
    {Jan. 2018 - Present} % Date(s)
    {\href{https://datalabsg.com}{datalabsg.com}} % Link
    {
      \begin{cvitems} % Description(s) of tasks/responsibilities
      \item {Design the software architecture of all projects.}
      \item {Create \& manage software infrastructure and policies.}
      \item {Ensure code quality of projects.}
      \end{cvitems}
    }
%---------------------------------------------------------
  \cventry
    {Frontend Developer \& Scrum Master} % Job title
    {Poverty Stoplight} % Organization
    {Asuncion, Paraguay} % Location
    {Oct. 2018 - Mar. 2019} % Date(s)
    {\href{https://povertystoplight.org}{povertystoplight.org}} % Link
    {
      \begin{cvitems} % Description(s) of tasks/responsibilities
      \item {Designed the architecture of the new Poverty Stoplight Platform.}
      \item {Organized and ran the daily standup meetings for a six person team.}
      \item {Built the new Poverty Stoplight web frontend.}
      \end{cvitems}
    }
%---------------------------------------------------------
  \cventry
    {Co-Founder \& Head Organizer} % Job title
    {Summer School by SHSG} % Organization
    {St. Gallen, Switzerland} % Location
    {Jan. 2018 - Sep. 2018} % Date(s)
    {\href{https://summerschool.shsg.ch}{summerschool.shsg.ch}} % Link
    {
      \begin{cvitems} % Description(s) of tasks/responsibilities
      \item {Organized a two week programming bootcamp for the students of the University of St. Gallen.}
      \item {Developed the curriculum.}
      \item {Fundraised CHF 40,000 for the bootcamp.}
      \item {Taught and mentored at the bootcamp.}
      \end{cvitems}
    }

%---------------------------------------------------------
%  \cventry
%    {Co-Curricular mentor} % Job title
%    {Institut Auf Dem Rosenberg} % Organization
%    {St. Gallen, Switzerland} % Location
%    {Jan. 2018 - Present} % Date(s)
%    {https://instrosenberg.com} % Link
%    {
%      \begin{cvitems} % Description(s) of tasks/responsibilities
%        \item {Teach 3D modelling \& printing as an extracurricular.}
%      \end{cvitems}
%    }
%---------------------------------------------------------
  \cventry
    {Chairman of IT \& Campus 2017-2018} % Job title
    {Studentenschaft der Universität St. Gallen (SHSG)} % Organization
    {St. Gallen, Switzerland} % Location
    {Jun. 2017 - May. 2018} % Date(s)
    {} % Link
    {
      \begin{cvitems} % Description(s) of tasks/responsibilities
        \item {Manage, Innovate the organization's digital \& physical resources.}
        \item {Implement a knowledge management system to help create permanence \& continuity to the organization's operations.}
        \item {Redeveloped the Kurskatalog, which helps students have easy access to course information for the bidding process.}
        \item {Responsible for a budget of CHF 65,000 and a team of 8 }
      \end{cvitems}
    }
%---------------------------------------------------------
  \cventry
    {Intern} % Job title
    {PAYRETO Philippines Inc.} % Organization
    {Makati, Philippines} % Location
    {Aug. 2013 - Apr. 2015} % Date(s)
    {\href{https://payreto.com}{payreto.com}} % Link
    {
      \begin{cvitems} % Description(s) of tasks/responsibilities
        \item {Developed an internal invoicing tool from conception to execution. The application takes employees time logs as an input and generates a pdf invoice for each client at the end of the month.}
        \item {Wrote scripts to automate internal processes.}
        \item {Assisted the company in obtaining PCI-DSS Level 1 Compliance.}
        \item {Assisted in managing and securing the IT Infrastructure (Network, Database and Server Administration).}
        \end{cvitems}
    }
%---------------------------------------------------------
  \cventry
    {Intern (Remote)} % Job title
    {IBM} % Organization
    {Manila, Philippines} % Location
    {Oct. 2014 - Feb. 2015} % Date(s)
    {} % Link
    {
      \begin{cvitems} % Description(s) of tasks/responsibilities
        \item {Provided support by creating modules for a resource management system servicing more than 430,000 IBMers, which resulted in global operations efficiency.}
        \item {Assisted in the maintenance and upgarde of several databases on an internal cloud infrastructure enabling fast distribution of data, accessible anytime, anywhere and on any device connected to the IBM intranet.}
      \end{cvitems}
    }

%---------------------------------------------------------
\end{cventries}
